Glyph-maps for Visualizing Climate Data and Models

### 2011-09-28 paper.tex
Restructure sections and update intro

In this paper we describe the algorithm for creating glyphs-maps, and various modifications that can enable different features in the data to be detected. Section~\ref{sec:large-data} describes how glyph-maps scale to large climate data sets, and Section~\ref{sec:construction} explains how to construct them. Section~\ref{sec:reference} discusses the use of reference lines and boxes, Section~\ref{sec:perception}, their perceptual properties, and Section~\ref{sec:scale} visits scaling issues. We originally developed glyph-maps for data on a rectangular grid, but many spatiotemporal data sets have irregular spatial locations. Section~\ref{sec:irregular} discusses how glyph-maps can be adjusted for this type of data.

>>>>

We begin in Section~\ref{sec:construction} by describing the algorithm used to create glyphs-maps. Section~\ref{sec:perception} discusses their perceptual properties, including the importance of a visual reference grid, and of carefully considering scale. Section~\ref{sec:large-data} shows how glyph-maps scale to large data, and the interplay of models with glyph-maps. We originally developed glyph-maps for data on a rectangular grid, but many spatiotemporal data sets have irregular spatial locations. Section~\ref{sec:irregular} discusses how glyph-maps can be adjusted for this type of data.
